\documentclass{article}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\usepackage{verbatim}


\begin{document}
Eric Buras 3/3/16 Master's Thesis Outline
\\
\section{Abstract}

$Lx=b$\\
$x = L^{-1}b$\\
$x = (P+T)^{-1}b$\\
$x = (P+USV)^{-1}b$\\
$x = (P^{-1}-P^{-1}U(S^{-1}+VP^{-1}U)^{-1}VP^{-1})b$\\
$x = P^{-1}b-P^{-1}U(S^{-1}+VP^{-1}U)^{-1}VP^{-1}b$\\

This is the reason I wrote the paper. Novel Algorithm built on Fan Chung graph partitioning for power law graphs. For a class of graphs can give fast inversion for graph laplacian. dont have a great characterization of this class of graphs

\section{Introduction}
Why is this graph laplacian problem important. Talk about PageRank and other "ranks" ie proteinrank, generank. read as much as i can about neural application. cite it here and mention it in talk.

\section{Background}
Already written first draft\\
probably needs a lot more depth in the literature review\\
probably more papers out there on graph laplacian solvers besides LAMG, CMG, and the Penn state people

\section{Methodology}
Fan Chung's local and global portion\\
multigrid on local portion and why it is optimal (cite gary miller multigrid on planar thing) (multigrid on meshes1984 achi brandt) (cite Ulrich Rude erlang and nuremberg 2015 sisc paper)\\
direct solve on sparse portion. low rank because its small\\
therefore use sherman morrisson woodberry linear algebra to combine\\
somewhere in here need to explain networkx and petsc i think?\\
if we write in C talk about how it is first implementation


\section{Results}
Complexity analysis of all the individual parts\\
how fast is splitting for n edges?\\
multigrid O(n)\\
direct sparse solve is ?\\
how many mat-mat, mat-vec multiplies in the sherman morrison\\
table of times for different size graphs\\
maybe try to get it on a cluster to parallelize, or maybe do this after initial thesis defense\\
maybe try to compare with LAMG in matlab\\

\section{Applications}
merge this into results
graph laplacian linear systems of different types\\
C. elegans neural network\\
proteins and genes\\
facebook social networks\\
others? electric grids?\\

\section{conclusions}
how did we compare to LAMG and CMG
our algorithm is arguably much simpler and cleaner. no heuristics
talk about what worked and didnt\\
what will be improved upon\\

\section{Bibiliography from bibtex file}
\bibliographystyle{plain}
\bibliography{mastersbib}
\end{document}
